\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{calc}
\usepackage[normalem]{ulem} % for underline

\geometry{
    a4paper,
    left=5mm,
    right=5mm,
    top=5mm,
    bottom=5mm,
}

% Color palette
\definecolor{primarycolor}{RGB}{0,119,181}
\definecolor{secondarycolor}{RGB}{102,102,102}

% Make all links black by default
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
}

% Section headings: black
\titleformat{\section}
  {\color{black}\large\bfseries}
  {}{0em}{}[\titlerule]

\titlespacing{\section}{0pt}{8pt}{4pt}

% Company macro
\newcommand{\company}[1]{{\normalsize\textbf{\color{primarycolor}#1}}}
\newcommand{\role}[1]{{\small\textbf{#1}}}

\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\newlength{\leftcolwidth}
\newlength{\rightcolwidth}
\newlength{\gapwidth}
\setlength{\leftcolwidth}{0.34\textwidth}
\setlength{\gapwidth}{0.03\textwidth}
\setlength{\rightcolwidth}{0.63\textwidth}

\begin{document}

\begin{center}
    {\fontsize{36}{20}\selectfont\textbf{Dibyajyoti Pradhan}}\\[0.4em]
    {\small \textbf{Senior Software Engineer} | Driving Development at
    \textbf{\textcolor{primarycolor}{\href{https://en.wikipedia.org/wiki/Meta_Platforms}{Meta}}},
    \textbf{\textcolor{primarycolor}{\href{https://en.wikipedia.org/wiki/HubSpot}{HubSpot}}} \&
    \textbf{\textcolor{primarycolor}{\href{https://en.wikipedia.org/wiki/Amazon_(company)}{Amazon}}}} |
    London, United Kingdom\\[0.4em]
    \href{tel:+447424781958}{\uline{+44-7424781958}} \quad
    \href{mailto:dibyajyotipradhan.official@gmail.com}{\uline{dibyajyotipradhan.official@gmail.com}} \quad
    \href{https://www.linkedin.com/in/dibyajyoti-pradhan-83a649146/}{\uline{LinkedIn}} \quad
    \href{https://github.com/Dibyajyoti-Pradhan}{\uline{GitHub}} \quad
    \href{https://dibyajyoti-pradhan.github.io/my-portfolio/}{\uline{Portfolio}}
\end{center}

\section*{Summary}
Senior Software Engineer with 6+ years of experience at Meta, Amazon, and HubSpot. Skilled in backend, frontend, and distributed systems, with expertise in system design, scalability, and performance optimization. Proven record of delivering high-impact solutions, mentoring engineers, and collaborating across product, design, and engineering.

\vspace

\noindent\begin{minipage}[t]{\leftcolwidth}

\section*{Skills}
\begin{itemize}[leftmargin=*,itemsep=0.3em]
    \small
    \item \textbf{Languages:} C, C++, Python, Java, JavaScript, TypeScript, Hack, SQL
    \item \textbf{Frameworks:} React, React Native, Spring, Spring MVC, Google Guice, Dagger 2.0, CHIRP RPC
    \item \textbf{Web Technologies:} HTML, CSS, GraphQL
    \item \textbf{Tools:} Git, Docker, Kubernetes, Kafka, AWS
    \item \textbf{Databases:} MongoDB, DynamoDB, Vitess DB, PostgreSQL, MySQL
    \item \textbf{AI:} LLM Integration (GPT-4o, Claude AI, Cursor, Copilot), Prompt Engineering, GenAI Applications
    \item \textbf{Other:} System Design, Scalable Architecture, RESTful APIs, Backend Development, Data Structures, Algorithms, Microservices, Agile, OOP, Design Patterns, Maven, CI/CD
\end{itemize}

\section*{Achievements}
\begin{itemize}[leftmargin=*,itemsep=0.3em]
    \small
    \item \textbf{GenAI Implementation:} Introduced GenAI (Llama 2) for Ad Creatives in AMA, enhancing ad creative capabilities.
    \item \textbf{Innovation Award:} Received the ``Most Innovative Award'' at the Amazon Pay EDH Hackathon for pioneering a near-zero latency model for the Amazon Pay For Business App.
    \item \textbf{Scholarship Recognition:} Recognized with the Jagadis Bose National Talent Search Scholarship, selected as one of 56 scholars from over 3000 applicants from top-tier colleges.
\end{itemize}

\section*{Education}
\textbf{Professional Certificate in Machine Learning \& AI}\\
\textit{Imperial College London} \\
2025 -- 2026 \quad \textit{In Progress · 25 Weeks}\\[0.3em]
\small Curriculum: Supervised/Unsupervised Learning, Neural Networks, Deep Learning, NLP, Reinforcement Learning, Recommender Systems, Deployment\\[0.2em]
Capstone Projects: \textit{Hull Tactical — S\&P 500 Market Prediction} (classification models on financial data); \textit{Black-Box Optimisation} (Bayesian optimisation with Gaussian Process surrogates)\\
\normalsize

\vspace{0.5em}
\textbf{Bachelor of Engineering in Electronics \& Telecommunication Engineering}\\
\textit{Jadavpur University} \\
2015 -- 2019 \quad \textit{Kolkata, India}

\end{minipage}%
\hfill%
\begin{minipage}[t]{\rightcolwidth}
\section*{Experience}

\company{HubSpot}

\role{Senior Software Engineer} \hfill 07/2024 -- Present\\
\small\textit{London, United Kingdom}

\begin{itemize}[leftmargin=*,itemsep=0.3em]
    \small
    \item Designed and built Account Insights, a real-time recommendation engine — driving 10\% user retention increase and 40\% platform adoption (highest across the platform).
    \item Architected GPT-4 powered audit log summarization — RPC infrastructure with JinJava templating and memcached caching, reducing enterprise security analysis from hours to minutes while processing 100k+ audit events with sub-second response.
    \item Built AI-powered admin agents using GPT-4o Copilot actions to automate cleanup of stale CRM assets (marketing emails, websites, etc.), reducing 70\% of recurring customer costs.
    \item Contributing to the Product Approvals platform --- building high-throughput, low-latency services for gated access, approval workflows, and audit trail integration across HubSpot products.
\end{itemize}

\vspace{0.5em}
\company{Meta}

\role{Software Engineer II} \hfill 04/2022 -- 05/2024\\
\small\textit{London, United Kingdom}

\begin{itemize}[leftmargin=*,itemsep=0.3em]
    \small
    \item Lead development of mid-flight recommendation flows, like Placements and Campaign Budget, within the Ads Manager App (AMA), resulting in a notable 0.04\% increase in Meta's top-line revenue weighted adoptions and over 12{,}000 weekly resolutions.
    \item Achieve a remarkable 20\% improvement in screen load times for 8 highly trafficked interfaces in AMA through efficient pre-fetching of relay queries, enhancing user experience.
    \item Revamp the duplication flow in AMA to align with ODAX objectives, resulting in a significant 14\% increase in revenue and an 18\% growth in ad duplications.
\end{itemize}

\vspace{0.5em}
\company{Amazon}

\role{Software Development Engineer -- 2} \hfill 10/2021 -- 02/2022\\
\small\textit{Hyderabad, India}

\begin{itemize}[leftmargin=*,itemsep=0.3em]
    \small
    \item Expanded user base of Amazon Pay for Business app by 5 million downloads and achieved a 4.3-star rating from launch. Optimized latency and resolved operational inefficiencies.
    \item Engineered an innovative `Offline Architecture' for the app, eliminating perceived latency.
    \item Streamlined crawler latency in Daily MIS Settlement Report, reducing processing time from 3 hours to 10 minutes, resolving delays for 70+ online and organized merchants.
    \item Provided mentorship to 3 developers.
\end{itemize}

\vspace{0.5em}
\company{Amazon}

\role{Software Development Engineer -- 1} \hfill 07/2019 -- 09/2021\\
\small\textit{Hyderabad, India}

\begin{itemize}[leftmargin=*,itemsep=0.3em]
    \small
    \item Orchestrated the development of 18 major pages for the Amazon Pay for Business app.
    \item Played the founding engineer role in a team of three, facilitating 5 million merchant engagements at launch.
\end{itemize}

\vspace{0.5em}
\company{Amazon}

\role{Software Development Engineer -- Intern} \hfill 05/2018 -- 07/2018\\
\small\textit{Hyderabad, India}

\begin{itemize}[leftmargin=*,itemsep=0.3em]
    \small
    \item Developed automation for sequence generation in a tier-1 service, benefiting over 100 developer teams in Amazon.
    \item Created a comprehensive full-stack admin tool to monitor and manage sequence configurations in real-time.
\end{itemize}

\end{minipage}

\end{document}
